Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2020-09-28 paper/paper_main.tex
re: restructuring the introduction
Deeksha's comments: single and wandering tone
edits to the acknowledgements and tidying up author list comments to get ready for circulation

\author{\han{to do: check names - initials?}}
\affiliation{%
\han{to do: check all affiliations}
}

@@

\begin{abstract}
Gravitational-wave observatories around the world are searching for continuous waves: persistent signals from spinning neutron stars. 
These searches use sophisticated statistical techniques to look for weak signals in noisy data. 
In this paper, we demonstrate these techniques using a table-top model gravitational-wave detector (a Michelson interferometer), where sound plays the role of gravitational waves. 
Using signal processing techniques from continuous-wave searches we demonstrate the recovery of tones with constant and wandering frequencies. 
Finally we use the interferometer as an `optical microphone' to capture music and speech and apply filtering techniques to recover the original signals from the noisy data. Such techniques include simple bandpass and notch filters, as well as comparing a Weiner filter to the statistical logMMSE method.  
Simple chords and drums are easily recovered, but complex music and speech are more challenging. 
This demonstration has scope for use in physics and electrical engineering undergraduate laboratories. 
It can also be adapted for use as an engagement tool for communicating gravitational-wave and signal-processing topics to non-specialist audiences. 
\end{abstract}

@@

\section{Constant tone}
\label{sec:single_tone}
\subfile{ifo-singleTone.tex}

\section{Wandering tone}
\label{sec:viterbi_wandering}
\subfile{ifo-wanderingTone.tex}

@@

\begin{acknowledgments}
The authors are grateful to Jude Prezens, Alex Tolotchkoc, and Blake Molyneux for their technical advice and generous assistance throughout the project. 
This research is supported by the Australian Research Council Centre of Excellence for Gravitational Wave Discovery (OzGrav) (project number CE170100004). 
This work also received financial support for hardware from the Institute of Physics International Member Grant and for travel from the Australian National University PhB Science program.

>>>>

%\author{\han{to do: check names - initials?}}
%\affiliation{%
%\han{to do: check all affiliations}
%}

@@

\begin{abstract}
Gravitational-wave observatories around the world are searching for continuous waves: persistent signals from spinning neutron stars. 
These searches use sophisticated statistical techniques to look for weak signals in noisy data. 
In this paper, we demonstrate these techniques using a table-top model gravitational-wave detector (a Michelson interferometer), where sound plays the role of gravitational waves. 
Using signal processing techniques from continuous-wave searches we demonstrate the recovery of tones with constant and wandering frequencies. 
Finally we use the interferometer as an `optical microphone' to capture music and speech and apply filtering techniques to recover the original signals from the noisy data. Such techniques include simple bandpass filtering, notch filters, a Weiner filter, and the statistical logMMSE method.  
Simple chords and drums are easily recovered, but complex music and speech are more challenging. 
This demonstration has scope for use in physics and electrical engineering undergraduate laboratories. 
It can also be adapted for use as an engagement tool for communicating gravitational-wave and signal-processing topics to non-specialist audiences. 
\end{abstract}

@@

\section{Constant frequency signal}
\label{sec:single_tone}
\subfile{ifo-singleTone.tex}

\section{Wandering frequency signal}
\label{sec:viterbi_wandering}
\subfile{ifo-wanderingTone.tex}

@@

\begin{acknowledgments}
The authors are grateful to Jude Prezens, Alex Tolotchkoc, and Blake Molyneux for their technical advice and generous assistance; Patrick Meyers, Margaret Millhouse, Sofia Suvorova for useful discussions; and Patrick Clearwater, Patrick Meyers, Suk Yee Yong, Lucy Strang, Julian Carlin, Sanjaykumar Patil, and Alex Cameron for early work on the interferometer design requirements and construction. 
This research is supported by the Australian Research Council Centre of Excellence for Gravitational Wave Discovery (OzGrav) (project number CE170100004). 
This work received financial support towards hardware from the Institute of Physics International Member Grant and the OzGrav Outreach Support scheme and travel support was received from the Australian National PhB Science program.
This work has been assigned LIGO document number P2000386.
